Sparse Function-space Representation \\ of Neural Networks

### 2023-05-14 paper/main.tex
updated intro to experiments

Our experiments seek to answer the following questions:
\begin{itemize}
  \item Does NN2SFR caputure good uncertainty estimates
\end{itemize}

>>>>

Our experiments seek to answer the following questions:
\begin{enumerate}
  \item \textbf{Predictions} How do predictions with our sparse function-space approximation compare to weight-space approximations? Does our method's ability to consider the full data set offer benefits over subset function-space methods?
  % \item Does our method's ability to consider the full data set offer benefits over subset function-space methods?
  \item \textbf{Function-space updates} How faster are our function-space updates relative to retraining from scratch? Do they improve predictive performance? Are they as good as retraining from scratch?
  \item \textbf{Uncertainty} How good are our uncertainty estimates? Can they be used in downstream settings like RL?
  \item \textbf{Representation} Is our sparse function-space representation useful for continual learning?
\end{enumerate}
